Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/impl.tex
do not mention the url due to anonymous submission
pass over impl

The current prototype of the Nail parser generator supports the C programming
language and top-down parsers. The implementation parses Nail grammars with Nail itself, using a 130
line Nail grammar feeding into a 2000 line C++ program that implements the parser. Bootstrapping is
performed with a subset of the grammar implemented using conventional grammars. 
Options for C++ STL data models and emitting
Packrat parsers~\cite{packrat-parsing:icfp02} are under development. In
this section, we will discuss some particular features of our parser
implementation.

The source code of our implementation, together with the examples described in
\S\ref{s:eval} are available on GitHub at \url{https://github.com/jbangert/nail}.

@@

Under this premise, the actions need limited information from the
recognizer to correctly handle the input stream. In particular, the parser's
control flow branches only at the choice, repetition, and constant combinators.
Thus, for each of those combinators, we store the minimum amount of information
required to reconstruct the syntactic structure of the input. The trace is an
array of integers.
Whenever the parser encounters a choice, it appends two integers to the trace. After it
successfully parses a choice, the parser writes the number of that choice and
the length of the trace when it began parsing that choice. When backtracking in
the input, the parser does not backtrack in the trace. This means that offsets
within the trace can be used for a Packrat hash-table to memoize backtrack-heavy
parsers.

When encountering a repetition combinator, the parser records the number of
times the inner parser succeeded, and when encountering a constant parser of
variable size, it records how much input was consumed by the constant parser.

>>>>

The current prototype of the Nail parser generator supports the C programming
language and top-down parsers. The implementation parses Nail grammars with Nail itself, using a
130-line Nail grammar feeding into a 2,000-line C++ program that
implements the parser. Bootstrapping is
performed with a subset of the grammar implemented using conventional grammars. 
Options for C++ STL data models and emitting
Packrat parsers~\cite{packrat-parsing:icfp02} are under development. In
this section, we will discuss some particular features of our parser
implementation.

% The source code of our implementation, together with the examples described in
% \S\ref{s:eval} are available on GitHub at \url{https://github.com/jbangert/nail}.

@@

Under this premise, the actions need limited information from the
recognizer to correctly handle the input stream. In particular, the parser's
control flow branches only at the choice, repetition, and constant combinators.
Thus, for each of those combinators, we store the minimum amount of information
required to reconstruct the syntactic structure of the input.

The trace is an
array of integers.
Whenever the parser encounters a choice, it appends two integers to the trace:
the number of that choice and
the length of the trace when it began parsing that choice. When backtracking in
the input, the parser does not backtrack in the trace. This means that offsets
within the trace can be used for a Packrat hash table to memoize backtrack-heavy
parsers.
When encountering a repetition combinator, the parser records the number of
times the inner parser succeeded, and when encountering a constant parser of
variable size, it records how much input was consumed by the constant parser.
